Curvature Enhancement With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes

### 2013-01-11 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

Over the last years several modeling techniques have been developed
to generate a variety of shapes that look natural and realistic\cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
complex interpolation techniques \cite{Sorkine2004,Zhou2005}.

Traditional methods for smoothing surfaces from coarse geometry, like
the Catmull-Clark, have become widely popular \cite{Catmull1978,Stam1998}.
These works generalize the uniform B-cubic splines knot insertion
to meshes, some of them adding some type of control, for instance
with the use of creases to produce sharp edges \cite{DeRose1998},
or the modification of vertex weight to locally control the zone of
influence \cite{Biermann2000}. Instead, the presented method performs
a feature enhancement of the model by parameterizing the surface curvature,
creating a family of different versions of the same object and therefore
preserving the detail of the original model and a realistic appearance.

On the other hand, many types of brushes have been developed to sculpt
meshes. Brushes that perform inflation end up by losing detail when
inflating the vertices \cite{Stanculescu2011}, in contrast the presented
method allows inflation of the mesh vertices by moving them towards
the opposite curvature direction, conserving the shape and sharp features
of the model.

@@

Unlike other methods, our method allows to use mixed arbitrary types
of mesh representation as triangles and quads, exploiting the basic
geometrical relationships facilitating and ensuring convergence of
the algorithm and similar shapes consistent with the original shape
against the other methods.

@@

Our approach is based on an extension of the Laplace Beltrami operator
for meshes composed by triangles and quads. Interest on meshes composed
by triangles and quads has increasing in recent years due to the flexibility
of modeling tools as Blender 3D \cite{blender}. Today many artists
manually connect vertices such that its edition allows a simple way
to perform animation processes and interpolation \cite{Mullen2007}.
For these reasons it is very important to develop an operator that
allows working with this type of mesh immediately, eliminating the
need to preprocessing the mesh to convert to triangles and losing
the original design made by users.

>>>>

Over the last years several, modeling techniques able to generate
a variety of realistic shapes, have been developed \cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
based methods however require to interact with a minimun number of
control points for any operation to be efficient, or in other words,
a unicity condition is introduced by demanding a smooth surface after
any of these shape operations. Hence, traditional modeling methods
for subdividing surfaces from coarse geometry have become widely popular
\cite{Catmull1978,Stam1998}. These works have generalized a uniform
B-cubic spline knot insertion to meshes, some of them adding some
type of control, for instance with the use of creases to produce sharp
edges \cite{DeRose1998}, or the modification of some vertex weights
to locally control the zone of influence \cite{Biermann2000}. Neverteless
these methods are difficult to deal with since they require a large
number of parameters and a very tedious customization. Instead, the
presented method requires a single parameter that controls the global
curvature, whereby it performs a curvature enhancement and shape exaggeration
of the model, creating a family of different versions of the same
object and therefore preserving the detail of the original model and
a realistic appearance.

The curvature enhancement and shape exaggeration can be used in the
sculpting proccess when inflating with a brush since current brushes
that perform inflation end up by losing detail when moving vertices
\cite{Stanculescu2011}, in contrast the presented method allows inflation
of the mesh vertices by moving them towards the reverse curvature
direction, conserving the shape and sharp features of the model.

Interest on meshes composed by triangles and quads has increasing
in recent years due to the flexibility of modeling tools as Blender
3D \cite{blender}. Today many artists manually connect vertices such
that its edition allows a simple way to perform animation processes
and interpolation \cite{Mullen2007}. For these reasons it is very
important to develop an operator that allows working with this type
of mesh immediately, eliminating the need to preprocessing the mesh
to convert to triangles and losing the original design made by users.

@@

@@

Our work presents an extension of the Laplace Beltrami operator for
hybrid quad/triangle meshes, allows using mixed arbitrary types of
mesh representation, exploiting the basic geometrical relationships
facilitating and ensuring convergence of the algorithm and similar
shapes consistent with the original shape against the other methods.
